---
title: "RDA Exam"
author: ""
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br><br>

### Overview

We will be using the three datasets:

- <a href=https://graderdata.s3.amazonaws.com/securities.txt target=_blank>securities.csv</a>
- <a href=https://graderdata.s3.amazonaws.com/fundamentals.txt>fundamentals.csv</a>
- <a href=https://graderdata.s3.amazonaws.com/prices-split-adjusted.txt>split adjusted price.csv</a>

They were adapted from the webpage <a href=https://www.kaggle.com/dgawlik/nyse target=_blank>New York Stock Exchange</a>, where the original raw data can be found.
<br><br><br>


#### Prob 1. Loading data

The csv file of split_adjusted_price.csv is saved in the url:

`url_adjusted = 'https://graderdata.s3.amazonaws.com/prices-split-adjusted.csv'`

Load the data into a dataframe, make sure that the `date` column is of a proper type.

**Hint**: The function `as.Date` might come in handy.

```{r, echo = F}
library(dplyr)
url_adjusted = 'https://graderdata.s3.amazonaws.com/prices-split-adjusted.csv'
adjusted = read.csv(url_adjusted)
adjusted$date <- adjusted$date %>% as.Date()
```

<br><br><br>

#### Prob 2. Missing values

The dataset `securities` is loaded for you. 
```{r}
securities = read.csv('https://graderdata.s3.amazonaws.com/securities.csv', na.strings = "")
```
How many missing values are there in the column `Date.first.added`?

```{r}
securities %>% select(Date.first.added) %>% is.na() %>% sum()
```

<br><br><br>

#### Prob 3. Join

The dataset `fundamentals` is loaded for you. Inner join `fundamentals` and `securities` on the ticker symbols. Save the answer into a variable, you will need it for the latter problems.

```{r}
fundamentals = read.csv('https://graderdata.s3.amazonaws.com/fundamentals.csv', na.strings = "", row.names=1)
```

```{r}
A = inner_join(fundamentals, securities, by=c("Ticker.Symbol"="Ticker.symbol"))
```

<br><br><br>

#### Prob 4. ggplot2

From the merged data frame from Prob 3., visualize the relation between `Earnings.Before.Interest.and.Tax` and `Total.Equity`.

```{r}
library(ggplot2)
```

```{r, echo=F}
Common.Stock = cut(A$Common.Stocks, breaks=quantile(A$Common.Stocks, probs=c(0, 0.25, 0.7, 1)), include.lowest=TRUE)


ggplot(data= A) + geom_point(aes(x= Total.Equity,
                                 y=Earnings.Before.Interest.and.Tax), alpha = 0.7)


```

<br><br><br>

#### Prob 5. ggplot2 (continue)

From the merged data frame from Prob 3., compare the `Accounts.Payable` for different `GICS.Sector`.

**Hint**: 
You **DO NOT** need to customize the plot for this exam. In real work, you might want to:

- Rotate the x-axis label to avoid overlapping by `+ theme(axis.text.x = element_text(angle = 90, hjust = 1))`
- Zoom in to neglect outliers by `+ ylim(NA, 5e10)`

```{r, echo=F}
ggplot(data= A) + geom_boxplot(aes(x=GICS.Sector, y=Accounts.Payable)) 
```

<br><br><br>

#### Prob 6. dplyr: Grouping and aggregating

From the merged data frame from Prob 3., find the `GICS.Sector` with the highest average `After.Tax.ROE`.

```{r}
library(dplyr)
```

```{r, echo=F}
A %>% group_by(GICS.Sector) %>% 
  summarise(avg_after_tax_roe = mean(After.Tax.ROE)) %>%
  arrange(desc(avg_after_tax_roe))
```

<br><br><br>
